Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
future work: serialization
Also, 1.0 being near actually implies problems needing a solution.

Although it is coming close to a 1.0 release, \sklearn is by no means finished.
At present, it does not support some classical machine learning tasks. Among
others, missing features include neural networks, ensemble meta-estimators for
bagging or subsampling strategies, or missing value completion algorithms.
Topics like structured prediction or reinforcement learning are however
considered off-topic for the project, since they would require quite different
data representations and API.

@@

>>>>

A \sklearn~1.0 release is nearing,
but several problems must still be resolved.
At present, the library does not support some classical machine learning tasks,
including neural networks, ensemble meta-estimators for
bagging or subsampling strategies and missing value completion algorithms.
Topics like structured prediction or reinforcement learning are
considered off-topic for the project, since they would require quite different
data representations and APIs.

@@

Finally, a long-term solution for model persistence is missing.
Currently, Python's \texttt{pickle} module is recommended for serialization,
but this only offers a file format,
not a way of preserving compatibility between versions.
Also, it has security problems because its deserializer
may execute arbitrary Python code,
so models from untrusted sources cannot be safely ``unpickled''.
